\section{Introduction}
\label{sec:intro}

Legal reasoning across jurisdictions presents a unique formal challenge:
concepts that are well-defined in one legal system (e.g., ``material breach''
in U.S. contract law) have no direct equivalent in another (e.g., Chinese
contract law under the Civil Code). Existing computational legal systems
typically rely on probabilistic retrieval-augmented generation (RAG), which
lacks formal guarantees about soundness, completeness, or cross-jurisdictional
consistency.

This paper presents \textbf{juris-calculus}, a symbolic legal reasoning engine
that operates across three jurisdictions---the People's Republic of China
(PRC), Hong Kong (HK), and the United States (US)---using deterministic
fixpoint evaluation rather than probabilistic language models.

\subsection{Contributions}

Our contributions fall into two categories: results \emph{formally verified}
in Lean~4~\cite{lean4}, and results established by complementary methods
(SMT, exhaustive enumeration, property-based testing) whose Lean
formalization is planned.

\begin{enumerate}[label=(\roman*)]
  \item \textbf{Finite monotone fixpoint theory}
        (\texttt{FiniteMonotoneIteration.lean}): We prove that any finite
        monotone system on a finite type has a fixed point reachable in
        $\leq |X|$ iterations (\texttt{exists\_fixpoint\_le\_card},
        \texttt{fixed\_at\_card}).

  \item \textbf{Dung abstract argumentation}
        (\texttt{DungFixedPoint.lean}): We formalize the grounded extension
        and prove existence, uniqueness, soundness, and completeness of the
        grounded labelling---16 theorems including
        \texttt{groundedSpec\_is\_least\_fixed\_point} and
        \texttt{self\_attack\_not\_in\_grounded}.

  \item \textbf{Horn logic fixpoints}
        (\texttt{HornDefinitions.lean}, \texttt{HornFixedPoint.lean}):
        We prove monotonicity, soundness, completeness, and minimality of
        the $T_H$ operator---12 theorems including
        \texttt{horn\_result\_least\_fixed\_point}.

  \item \textbf{Banach contraction (effective nodes)}
        (\texttt{BanachEffectiveNodes.lean}, \texttt{WeightedSupNorm.lean},
        \texttt{ContractionCondition.lean}): For a finite pricing function
        $\text{pricingFn}(x) = \beta T + (1{-}\beta)x$, we prove the
        weighted sup-norm is a metric, and the map is a contraction with
        unique fixed point.

  \item \textbf{Unified composition}
        (\texttt{UnifiedModel.lean}): We prove soundness of the two-stage
        evaluator (Horn then AAF), a full chain theorem, and a Galois
        connection completeness result.

  \item \textbf{Obstruction theory}
        (\texttt{FiniteRosetta.lean}): We prove that no total functor
        exists for the toy Rosetta model and that the obstruction density
        exceeds $2/3$.

  \item \textbf{Temporal invariants}
        (\texttt{TemporalKripke.lean}): We prove the temporal guard
        $\square(t_f < t_p)$ always holds and that litigation always
        satisfies the guard.

  \item \textbf{Planned work}: Full-dimensional Banach contraction,
        real-data Rosetta functor, DP $\varepsilon$ determinability,
        and general AAF convergence for $n > 4$ remain open or
        data-insufficient.
\end{enumerate}

\subsection{Research Methodology}

This work employs an iterative AI-assisted methodology: Claude (Anthropic)
performed initial modeling; Codex~\cite{codex2026} (OpenAI) conducted
formal verification using Lean~4, Z3~\cite{z3}, and Hypothesis; a second
Codex audit downgraded overstated claims. The evidence-calibrated trust
label system (Section~\ref{sec:trust}) records which tool produced which
evidence.

\subsection{Paper Structure}

Sections~\ref{sec:prelim}--\ref{sec:ontology} establish notation and the
legal ontology. Sections~\ref{sec:horn}--\ref{sec:evaluator} formalize
the two-stage evaluator. Sections~\ref{sec:kripke}--\ref{sec:banach}
develop the temporal, categorical, and analytic models.
Sections~\ref{sec:dp}--\ref{sec:trust} address privacy, non-interference,
and the trust label system. Section~\ref{sec:conclusion} summarizes
contributions, open problems, and future directions.
