\section{Banach Pricing Contraction}
\label{sec:banach}

The LegalOS pricing model attempts to estimate legal service costs using a
fixpoint iteration. This section analyzes whether the pricing map satisfies
the Banach contraction property.

\subsection{Pricing Map Definition}

\begin{definition}[Effective-node pricing map]
The pricing map $T: M \to M$ on the effective-node space is defined as:
\begin{equation}
  T(x) = \beta \cdot C + (1 - \beta) \cdot x
  \label{eq:pricing-map}
\end{equation}
where:
\begin{itemize}
  \item $x \in M$ is the current price estimate;
  \item $C$ is the observed cost (from timesheet data);
  \item $\beta \in (0, 1)$ is the smoothing parameter.
\end{itemize}
\end{definition}

\subsection{Single-Dimensional Contraction}

\begin{theorem}[Scalar contraction for effective nodes]
\label{thm:banach-scalar}
For the single-dimensional case $M = \Real$ with $d(x, y) = |x - y|$,
the pricing map~\eqref{eq:pricing-map} is a $\beta$-contraction:
\begin{equation}
  |T(x) - T(y)| = |(1 - \beta)(x - y)| = (1 - \beta)|x - y|
\end{equation}
Since $\beta \in (0, 1)$, we have $1 - \beta \in (0, 1)$, confirming
contraction with constant $1 - \beta < 1$.
\end{theorem}

\begin{proof}
By SymPy symbolic computation. The script
\texttt{banach\_effective\_nodes.py} verifies:
\begin{enumerate}
  \item $|T(x) - T(y)| = (1 - \beta)|x - y|$ (symbolic identity);
  \item The unique fixed point is $x^* = C$ (the observed cost);
  \item Convergence from any initial $x_0$ requires
        $O(\log(1/\varepsilon))$ iterations.
\end{enumerate}
\end{proof}

\begin{corollary}[Unique pricing fixpoint]
The pricing map has a unique fixed point $x^* = C$, which is the
observed cost. Any initial estimate converges to $C$.
\end{corollary}

\subsection{Full-Dimensional Counterexample}

\begin{counterexample}[Full-dimensional Banach: metric space undefined]
\label{ce:banach-full}
The Banach contraction property \textbf{cannot} be claimed for the
full-dimensional pricing model because:
\begin{enumerate}
  \item The pricing space has multiple dimensions (hours, rate, complexity,
        jurisdiction), but no metric $d$ is defined on this space;
  \item The variable \texttt{mapping\_status} is a discrete nominal label
        (e.g., ``approved'', ``pending''), not a point in a metric space;
  \item The existing 225 pricing observations are all fee-schedule proxies
        (0 real timesheets, 0 invoices), making the empirical Lipschitz
        ratio meaningless.
\end{enumerate}
\end{counterexample}

\begin{remark}
The single-dimensional contraction (Theorem~\ref{thm:banach-scalar}) is a
valid toy model. The full-dimensional claim requires:
\begin{enumerate}
  \item A well-defined metric on the multi-dimensional pricing space;
  \item Real timesheet data (not fee-schedule proxies);
  \item Empirical verification of the Lipschitz constant.
\end{enumerate}
None of these prerequisites are currently satisfied.
\end{remark}
