\section{Conclusion and Open Problems}
\label{sec:conclusion}

\subsection{Summary of Contributions}

This paper presents a formal mathematical framework for cross-jurisdictional
symbolic legal reasoning. The key contributions are:

\begin{enumerate}
  \item A \textbf{three-layer legal ontology} ($L_0$/$L_1$/$L_2$) with
        formal definitions of 6 primitives, 15 meta-ontological categories,
        and 20+ domain concepts (Section~\ref{sec:ontology});
  \item \textbf{Horn closure monotonicity} and \textbf{bounded correctness}
        proved analytically and verified over 82,836 test cases
        (Section~\ref{sec:horn});
  \item \textbf{Dung AAF grounded extension} existence and uniqueness proved
        by exhaustive enumeration over 66,066 attack graphs
        (Section~\ref{sec:aaf});
  \item \textbf{Kripke temporal invariants} including mutual exclusion and
        the $\square(t_f < t_p)$ guard, verified by Z3 SMT solving
        (Section~\ref{sec:kripke});
  \item \textbf{10 explicit counterexamples} refuting claims about evaluator
        monotonicity, DP epsilon determinability, graph similarity metricity,
        and full-dimensional Banach contraction
        (Sections~\ref{sec:evaluator}--\ref{sec:dp});
  \item A 7-level \textbf{evidence-calibrated trust label system} that
        tracks every claim through its proof lifecycle
        (Section~\ref{sec:trust});
  \item \textbf{All proof artifacts are machine-reproducible} via Python
        scripts with Lean~4, Z3, Hypothesis, and SymPy verification.
\end{enumerate}

\subsection{Theorem Status Table}

\begin{table}[h]
\centering
\small
\begin{tabular}{@{}llcl@{}}
\toprule
\textbf{ID} & \textbf{Theorem/Claim} & \textbf{Status} & \textbf{Method} \\
\midrule
T\ref{thm:horn-correct} & Bounded Horn correctness & $\checkmark$ & Enumeration \\
T\ref{thm:horn-mono} & Horn monotonicity & $\checkmark$ & Analytic \\
T\ref{thm:horn-pbt} & Horn 5 properties & $\checkmark$ & PBT (82,836) \\
T\ref{thm:aaf-ge} & AAF grounded extension & $\checkmark$ & Enumeration (66,066) \\
P\ref{prop:stratified} & Stratified correspondence & $\checkmark$ & Enumeration (14) \\
T\ref{thm:stage1} & Stage 1 monotone & $\checkmark$ & Analytic \\
T\ref{thm:stage2} & Stage 2 deterministic & $\checkmark$ & Enumeration (10) \\
T\ref{thm:stage3a} & Stage 3a convergence & $\checkmark$ & T\ref{thm:aaf-ge} \\
T\ref{thm:op-termination} & 5 operational bounds & $\checkmark$ & Enumeration (5) \\
T\ref{thm:kripke-mutex} & Kripke mutex & $\checkmark$ & Z3 UNSAT \\
T\ref{thm:temporal-guard} & $\square(t_f < t_p)$ & $\checkmark$ & Z3 induction \\
T\ref{thm:rosetta-toy} & Toy Rosetta & $\checkmark$ & Enumeration (243) \\
T\ref{thm:rosetta-real} & Real Rosetta & $\triangle$ & 44 rows only \\
T\ref{thm:banach-scalar} & Scalar Banach & $\checkmark$ & SymPy \\
T\ref{thm:dp-cn} & CN no monotone $\varepsilon$ & $\checkmark$ & Z3 UNSAT \\
T\ref{thm:cbl-ni} & CBL = non-interference & $\checkmark$ & Structural \\
T\ref{thm:trust-consistency} & Trust label consistency & $\checkmark$ & Program \\
\midrule
CE\ref{ce:eval-mono} & Evaluator monotone & $\times$ & Counterexample \\
CE\ref{ce:stage3b} & Cross-graph monotone & $\times$ & Counterexample \\
CE\ref{ce:banach-full} & Full Banach metric & $\times$ & Undefined \\
CE\ref{ce:dp-cross} & Cross-jurisdiction $\varepsilon$ & $\times$ & 2-model \\
CE\ref{ce:dp-floor} & Floor clipping $\varepsilon$-DP & $\times$ & $\infty$-ratio \\
\bottomrule
\end{tabular}
\caption{Complete theorem status. $\checkmark$: proved/verified.
$\triangle$: data-insufficient. $\times$: refuted.}
\label{tab:theorem-status}
\end{table}

\subsection{Extended Theoretical Foundations}

The juris-calculus theory module contains additional formalizations not
covered in the main body of this paper. We list them here with their
evidence status for completeness:

\begin{enumerate}
  \item \textbf{Counts-As Institutional Facts}~\cite{searle1995,hart1961}.
        Formalizes Searle's ``$X$ counts as $Y$ in context $C$'' and
        Hart's rule of recognition within the compiler architecture.
        Maps physical tokens (signed PDFs) to legal facts (contract
        formation) through context-dependent type promotion.
        Status: \textsc{Engineering\_Baseline}.

  \item \textbf{Discretionary Concepts as Rough Sets}~\cite{pawlak1982}.
        Models 16 discretionary legal concepts (e.g., ``reasonable'',
        ``proportionate'') using Pawlak's rough set theory, replacing
        the binary TAINTED marker with a rough membership function.
        Status: \textsc{Engineering\_Baseline}.

  \item \textbf{Procedural Justice as Deontic Logic}~\cite{deontic}.
        Reinterprets 10 procedural justice defense rules as deontic
        statements in Standard Deontic Logic with temporal operators.
        Status: \textsc{Engineering\_Baseline}.

  \item \textbf{Paradigm Incommensurability}~\cite{stevens1946}.
        Proves that LLM-as-Judge (ordinal scale) and symbolic
        confidence (ratio scale) are measurement-theoretically
        incommensurable under Stevens' typology.
        Status: \textsc{Engineering\_Baseline}.

  \item \textbf{Compiler as Abstract Interpretation}~\cite{cousot1977}.
        Reframes the 5-stage juris-calculus compiler as an instance
        of Cousot \& Cousot abstract interpretation. Currently an
        architectural catalog, not a standalone proof.
        Status: \textsc{Engineering\_Baseline}.

  \item \textbf{Exception Chain Depth as Kolmogorov Complexity}~\cite{kolmogorov1965}.
        Connects rule structural complexity to Minimum Description
        Length, explaining why single-premise rules have the highest
        cross-domain false-triggering rate.
        Status: \textsc{Conjecture}.
\end{enumerate}

These modules provide theoretical scaffolding for the core results
presented in Sections~\ref{sec:horn}--\ref{sec:noninterference} and
are available as runnable Python code in the \texttt{theory/} directory.

\subsection{Open Problems}

\begin{openproblem}[Full evaluator equivalence]
\label{op:eval-equiv}
Does the stratified evaluator (Horn then AAF) produce identical output to
the original combined evaluator for all production rules? This is the
most important open question for the juris-calculus architecture.
\end{openproblem}

\begin{openproblem}[General AAF convergence]
\label{op:aaf-general}
Does the Dung grounded extension converge for all finite $n$ (not just
$n \leq 4$)? While the theoretical answer is yes (by Tarski's theorem on
complete lattices), the \emph{operational} convergence bound for the
legal argument construction remains open.
\end{openproblem}

\begin{openproblem}[Real-data Rosetta functor]
\label{op:rosetta-real}
Does a total semantic-preserving functor exist for the complete PRC/HK/US
legal inventory? The current 44-row dataset is insufficient. A dataset of
$\geq 2{,}000$ cross-jurisdiction concept pairs would be needed.
\end{openproblem}

\begin{openproblem}[Full-dimensional Banach pricing]
\label{op:banach-full}
Can the pricing map be extended to a full-dimensional Banach contraction
with a well-defined metric and real timesheet data?
\end{openproblem}

\begin{openproblem}[Lean formalization]
\label{op:lean}
Three Lean~4 drafts exist (FiniteRosetta, BanachEffectiveNodes,
FiniteGaloisAdjunction) but contain \texttt{sorry} placeholders and
require Mathlib. Completing these formalizations would elevate the
trust labels from \textsc{Exhaustive\_Enumeration} to
\textsc{Lean\_Proved}.
\end{openproblem}

\subsection{Broader Impact}

The evidence-calibrated trust label system is applicable beyond legal
reasoning. Any domain where AI agents produce mathematical claims
(e.g., drug discovery, materials science, financial modeling) can adopt
this system to prevent the ``hallucination-to-production'' pipeline where
unverified AI assertions become engineering invariants.

The key principle is simple: \textbf{the strongest claim you can make is
the one your evidence supports---and no stronger.}
